CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-09-18 paper.Rmd
and --> and/or

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(e.g., continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
In addition, the [PFUAggDatabase][link-pfuaggdatabase] pipeline 
calculates efficiencies for each country
at all available aggregations.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.

>>>>

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(e.g., continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and/or end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
In addition, the [PFUAggDatabase][link-pfuaggdatabase] pipeline 
calculates efficiencies for each country
at all available aggregations.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.
